Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-07 paper/paper.tex
#22 write banger first paragraph

@@

@@

>>>>

The history of Europe was defined by conflict. No other continent at any time experienced more war than Europe in the early modern era (\citealp{voigtlnder2013}, p. 174). Wars brought death and devastation to the societies affected by them, but their effects also manifested on the political map --- they play out in a diverse ecosystem of polities that come and go and change size over time as the borders get redrawn and territory changes hands. One can indeed imagine this as an evolutionary process: states compete for resources and powerful states eventually absorb weaker ones. As a result, traits that increase state power --- the ability to win conflicts against rivals --- get selected for, while other traits are doomed to disappear \citep{levine2013, levine2021}.

In this paper I study the role of this process in the economic development of Europe. In particular, I estimate the effect of state power, the trait that conflict selects for, on urban development.

@@

Key motivation papers: \cite{levine2013, levine2021}, \cite{diamond1997}, \cite{schoenholzer2022}, \cite{cervellati2022}, \cite{voigtlnder2013}, \cite{tilly1985}

The idea that today's states are just the most successful protection rackets of the past already shows up in \cite{tilly1985}.

@@

\section{Historical Background}
